---
title: "House Price Prediction"
author: "Avalon"
date: "2017/1/9"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(plyr)
library(pipeR)
library(ggplot2)
```

## Loading data and check missing value distribution

```{r loaddata, echo = FALSE, warning = FALSE}
traindata <- fread("train.csv", stringsAsFactors = TRUE)
testdata <- fread("test.csv", stringsAsFactors = TRUE)
mergedata <- rbind.fill(traindata, testdata) %>>% setDT
tmpfile <- mergedata[, -"SalePrice", with = FALSE]
tmpfile <- ifelse(is.na(tmpfile), 1, 0)
tmpfile2 <- expand.grid(x = 1 : nrow(tmpfile), y = colnames(tmpfile)) %>>% setDT
tmpfile2$trans <- as.vector(tmpfile)
tmpfile2 <- tmpfile2[y %in% tmpfile2[, all(trans == 0), y][V1 == FALSE, y]]
ggplot(tmpfile2, aes(x, y, fill = as.factor(trans))) + geom_tile() + 
  scale_fill_manual(values = c("white", "black"),
                    name = "Missing Value\n0 = NO 1 = YES")
```

## Analyzing the factor MsSubClass
Definitions : Identifies the type of dwelling involved in the sale

```{r, echo = FALSE}
mergedata <- mergedata[, MSSubClass := as.factor(MSSubClass)]
mergedata[, .(number = .N), MSSubClass][order(-number)] %>>%
  ggplot(aes(MSSubClass, number, fill = MSSubClass)) + geom_bar(stat = "identity") +
  theme_bw()
traindata[, .(mean = mean(SalePrice, na.rm = TRUE),
              median = median(SalePrice, na.rm = TRUE)), MSSubClass][
                ,MSSubClass := as.factor(MSSubClass)] %>>%
  ggplot(aes(MSSubClass, mean, fill = MSSubClass)) + geom_bar(stat = "identity") +
  theme_bw()

```

## Analyzing the MSZoning

Definitions : Identifies the general zoning classification of the sale  
Something weird is there is a category called A representing agriculture.
However, it seems that A does not exist in the list of the categories.  
RP and I categories react the same way as well. Only testdata contains NA value.

```{r MSZoning, echo = FALSE, warning = FALSE}
mergedata[, .(number = .N), MSZoning] %>>% ggplot(aes(MSZoning, number,
                fill = MSZoning)) + geom_bar(stat = "identity") + theme_bw()
traindata[, .(mean = mean(SalePrice)), MSZoning] %>>% ggplot(aes(MSZoning, mean,
                fill = MSZoning)) + geom_bar(stat = "identity") + theme_bw()
```

## Analyzing The LotFrontage

Definitions : Linear feet of street connected to property  
Viewing the distribution of entire vector except missing value  
It seems that tremendous missing values in LotFrontage vector does not relate to
the average value of it, but the median value seems to be a little bit larger
while the data in LogFrontage is missing. Hence, this indicates that the missing
section contain much more higher value.
```{r LotFrontage, echo = FALSE, warning = FALSE}
ggplot(data = traindata, aes(LotFrontage)) + geom_density(fill = "skyblue") +
  scale_x_continuous(breaks = seq(0, 300, by = 50)) + theme_bw()
traindata[, .(mean = mean(SalePrice), median = median(SalePrice)),
          .(NAornot = is.na(LotFrontage))]
```

## Analyzing LotArea
Definitions : Lot size in square feet  
There are 14 outliers whose value are greater than 50000 feat squares, I set
the limitation of the plot on 50000. The maximum value is 200000.  
In general, we would assume that the size of lot is highly correlate with the
sale price. Nonetheless, the stength correlation does not support this 
hypothesis.After all, the relationship between size of Lot and sale price is positive.

```{r LotArea, echo = FALSE, warning = FALSE}
ggplot(data = mergedata, aes(LotArea)) + geom_density(fill = "brown") + 
  scale_x_continuous(limits = c(0, 50000)) + theme_bw()
cor(traindata$LotArea, traindata$SalePrice)
```

## Analyzing Street
Definitions : Type of road access to property  
This factor is an awkward factor. It contains only 12 Grvl while other is pave.
All in all, the street within Grvl might be much rougher or somewhat. The 
sale price in Grvl is much more cheaper than the one in pave. Hence, this factor
could be a strong preditor.
```{r Street, echo = FALSE}
mergedata[, .(number = .N), Street]
traindata[, .(mean = mean(SalePrice), median = median(SalePrice)), Street]
```

## Analyzing Alley
Definitions : Type of alley access to property  
I don't know if it is a coincidence that the house with a neiborhood with Grvl
has reletively low mean sale price. This matchs the circumstance that the house
in Grvl has relatively low sale price as well. However, the houses with no 
neiborhood are majority and it shows no giant difference with the houses with 
pave
```{r, echo = FALSE}
mergedata[, .(number = .N), Alley]
traindata[, .(mean = mean(SalePrice), median = median(SalePrice)), Alley]
```

## Analyzing LotShape
Definitions : General shape of property
Firstly, I think the LotShape doesn't matter, but it seems like that the most 
expensive objects are always with IR1 shape lot.  
Even though mean and median in Reg shape lot are relatively low, there are still
tremendous outliers.
```{r, echo = FALSE}
ggplot(data = traindata, aes(LotShape, SalePrice)) + geom_boxplot()
```

## Analyzing LandContour
Definitions : Flatness of the property   
Conspicuously, the houses with Bnk has very stable low sale price. Inspite of
the fact that mean and median in LVl are relatively low, there are numerous 
outliers in LVl.
```{r, echo = FALSE}
mergedata[, .(number = .N), LandContour]
ggplot(data = traindata, aes(LandContour, SalePrice)) + geom_boxplot()
```

## Analyzing Utilities
Definitions : Type of utilities available  
After see the distribution of the feature. Set a hot coded feature might be a
good way to explain it. Ther is only one house without water supply. Also, there
are two NA value.
```{r, echo = FALSE}
mergedata[, .(Number = .N), Utilities]
traindata[, .(Number = .N), Utilities]
```

## Analyzing LotConfig
Definitions : Lot configuration
```{r, echo = FALSE}
ggplot(traindata, aes(as.factor(LotConfig), SalePrice)) + geom_boxplot() +
  labs(x = "LotConfig")
```

